Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Describe verifiable counting in Scantegrity

>>>>

In order to preserve ballot secrecy, it must be impossible for anyone -- including a voter
him/herself -- to match published vote information (encrypted ballot or a hash) to its inclusion in
the final tally, as this would reveal the candidate for which the ballot was cast. As such, these
systems verify the accuracy of their counting indirectly by instilling in auditors confidence that
the tallying mechanisms are correct.

Scantegrity relies on unused \term{audit ballots} to prove that its Tables Q, R, and S accurately
match ballot selections with the proper candidates. These ballots come in two forms: a group of
ballots randomly selected and checked prior to the election by members of the election authority;
and the collection of optional secondary ballots that are offered to voters.

Auditing is then performed by revealing all bubble codes on the ballots and uncovering the entire
R-to-S mapping in Table Q for all rows corresponding to those revealed codes. An auditor then
manually examine the revealed information and ensure that, had a code been revealed as on a counted
ballot, the tally would have been affected appropriately. Note that this method of verification is
indirect in that it does not allow \emph{any} of the ballots that are cast during the election to be
verified, for reasons previously stated. Rather, it is expected that the random selection of ballots
beforehand, along with the selection of ballots chosen by voters as audit ballots, is a sufficient
sample to detect improper counting. Thus, if these checks past, it is accepted that all other
ballots must also be counted properly.

It is important to note that in order for this assurance to hold, the predetermined Tables cannot be
modified after they are initially created (prior to \emph{any} auditing). Through some means, the
election authority must therefore \term{commit} to the predetermined tables such that any change to
the data is either impossible or detectable.
